Title Goes Here

### 2024-05-24 analysis/paper/paper.qmd
exploring EEO words

# this doesn't work, need help to troubleshoot
EEO_word <- EEO_clean %>%
   unnest_tokens(word, 
                 equal_employment_opportunity_statement) %>%
  anti_join(get_stopwords()) %>%
  count(word, sort = TRUE)

# here's the list of words of interest
community_word <- c("women","color","religion","race","age","veteran","disability")

@@

# detect if the words of interest is present or not.
EEO_clean_community_word <- 
  bind_cols(EEO_clean, df) %>% 
  rowwise() %>% 
  mutate(community_word_tally = sum(c_across(all_of(community_word)), 
                                    na.rm = T))

@@

EEO_word %>% 
  filter(n >= 20) %>% 
ggplot() +
  aes(x = reorder(word, n), y = n) +
  geom_col() +
  coord_flip() +  # Flips the axes for easier reading of text
  labs(x = "Words", y = "Frequency", title = "Word Frequency") 
```

>>>>

EEO_word <- EEO_clean %>%
   unnest_tokens(word, 
                 equal_employment_opportunity_statement) %>%
  anti_join(get_stopwords()) %>%
  count(word, sort = TRUE) %>%
  drop_na()

# here's the list of words of interest
community_word <-
  c(
    "women",
    "color",
    "religion",
    "race",
    "age",
    "veteran",
    "disability",
    "citizenship",
    "ancestry",
    "national origin",
    "sex",
    "gender",
    "marital status",
    "genetic information",
    "breastfeeding",
    "sexual orientation",
    "transgender status",
    "gender expression"
  )

@@

# detect if the words of interest is present or not.
EEO_clean_community_word <- 
  bind_cols(EEO_clean, df) %>% 
  rowwise() %>% 
  mutate(community_word_tally = sum(c_across(all_of(community_word)), 
                                    na.rm = T)) %>% 
  bind_cols(EEO_wordcount) %>% 
  mutate(eeo_words_total_ratio = community_word_tally / word_count)

ggplot(EEO_clean_community_word) +
  aes(community_word_tally,
      word_count,
      size = eeo_words_total_ratio) +
  geom_point()

@@

```{r}
ggplot(EEO_word %>% 
         filter(n > 20), 
       aes(x = reorder(word, n), 
           y = n)) +
  geom_col() +
  labs(x = "Words", 
       y = "Frequency", 
       title = "Word Frequency") +
  coord_flip()
```
